A Detection of the Environmental Dependence of the Stellar Profiles and Halos of Massive Central Galaxies

### 2017-07-10 draft/paper2.tex
Figure 1

%%%%%%%%%%%%: Title and Affiliations %%%%%%%%%%%%

%% ------------------------------------------------------------------------------------ %% 
\title[Structure and Environment of Massive Galaxies]{A Detection of the Environmental 
       Dependence of the Stellar Profiles and Halos of Massive Central Galaxies}

@@

%%%%%%%%%%%%: Header and Version %%%%%%%%%%%%
\begin{document}

@@

%%%%%%%%%%%%: Abstract and Keywords %%%%%%%%%%%%

@@

%%%%%%%%%%%%: Main Text %%%%%%%%%%%%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_m100_m10_compare}
      \caption{
          Three-color images for a subsample of massive galaxies at $z{\sim}0.4$. 
          All of these galaxies have the same mass within a 10 kpc aperture 
          ($11.2<\log (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.3$). 
          The dash-line circle at the top-left figure indicates 10 kpc.
          Galaxies are rank-ordered from top to bottom and from left to right by 
          their \mstar{} within a 100 kpc aperture which varies from $10^{11.2} M_{\odot}$ 
          to $10^{11.7} M_{\odot}$. 
          At fixed ``inner'' mass ($M_{\star,10}$), massive galaxies display significant
          diversity in their outer profiles. 
          Red boxes indicate galaxies in halos more massive than 
          ${\sim} 10^{14.0} M_{\odot}$. 
          }
      \label{fig:m100_m10_color}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\section{Introduction}
    \label{sec:intro}

>>>>

%% ------------------------------------------------------------------------------------ %% 
%% Title and Affiliations 
%% ------------------------------------------------------------------------------------ %%

\title[Structure and Environment of Massive Galaxies]{
       A Detection of the Environmental Dependence of the Stellar Profiles and Halos
       of Massive Central Galaxies}

@@

%% ------------------------------------------------------------------------------------ %% 
%% Header and Version 
%% ------------------------------------------------------------------------------------ %%

\begin{document}

@@

%% ------------------------------------------------------------------------------------ %% 
%% Abstract and Keywords 
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
%% Main Text
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_m100_m10_compare}
      \caption{
          Three-color images for a subsample of massive galaxies at $z{\sim}0.4$. 
          All of these massive galaxies have very similar \mstar{} within a 10 kpc 
          elliptical aperture 
          ($11.2<\log (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.3$). 
          The dash-line circle at the top-left figure indicates $R=$10 kpc.
          These galaxies are rank-ordered from top to bottom and from left to right 
          by their \mstar{} within a 100 kpc elliptical aperture which varies 
          from $10^{11.2} M_{\odot}$ to $10^{11.7} M_{\odot}$. 
          At fixed ``inner'' mass (\minn{}), massive galaxies display significant
          diversity in their outer profiles. 
          Red boxes indicate galaxies from dark matter haloes that are more massive 
          than ${\sim} 10^{14.0} M_{\odot}$. 
          }
      \label{fig:m100_m10_color}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
%% Introduction 
%% ------------------------------------------------------------------------------------ %%

\section{Introduction}
    \label{sec:intro}
